\section{Definitions, acronyms and abbreviations}

\subsection{Definitions}
	\begin{labeling}{defs}
		\item[\textbf{Onboard computer}] An onboard computer is intend to be the embedded device integrated in the car system that provide two main functions: on one hand it shows the user basic information about the ongoing rental, on the other hand it is in charge of all the communications related to the state of the car between the car and the PowerEnJoy management system.
		\item[\textbf{Safe area}] A safe area is an area, within predefined edges, in which the users are allowed to park the rented cars. The users is not allowed to park, and therefore end a rental, if he/she is not inside a safe area.
		\item[\textbf{Special parking area}] A special parking area is a safe area where an electric car charging system is installed.
		\item[\textbf{Car states}] One and only one of the four following states is assigned to each car:
			\begin{labeling}{car-states}
				\item[\textbf{AVAILABLE}] A car is AVAILABLE when is parked in a safe area and can be booked by a user. It changes to RESERVED when a user books it or to UNAVAILABLE if it gets damaged.
				\item[\textbf{RESERVED}] A car is RESERVED when a user has booked it. This means that it cannot be booked by any other user until it becomes AVAILABLE again. A RESERVED car changes to AVAILABLE if the booking is canceled, to IN USE if the user that has booked it begins the rental, or to UNAVAILABLE if it gets damaged.
				\item[\textbf{IN USE}] A car is IN USE when a user is driving it. A car that is IN USE changes to AVAILABLE when the rental ends or to UNAVAILABLE if one of the conditions written below subsists.
				\item[\textbf{UNAVAILABLE}] A car is UNAVAILABLE if it's parked in a safe area with low battery (\textless\ 20\%), if the battery is completely exhausted or if the car is damaged. An UNAVAILABLE car changes to AVAILABLE only after being recovered by an external company in order to fix, depending on the situation, all problems written above.
			\end{labeling}
		\item[\textbf{Over-The-Air updates}] An Over-The-Air update is the wireless delivery of new software or data to mobile phones and tablets.
		\item[\textbf{Sign up}] Sign up is intended to be the registration phase. During this process, the user provides the system the credentials required along with the information about the documents required.
	\end{labeling}

\subsection{Acronyms}
	\begin{labeling}{acro}
		\item[\textbf{API}] Application Programming Interface
		\item[\textbf{GPS}] Global Positioning System
		\item[\textbf{OTA}] Over-The-Air
		\item[\textbf{PIN}] Personal Identification Number
		\item[\textbf{UML}] Unified Modeling Language
	\end{labeling}

\subsection{Abbreviations}
	\begin{labeling}{abbrv}
		\item[\textbf{24/7}] 24 hours a day, 7 days a week.
		\item[\textbf{ID}] Identification
	\end{labeling}