\section{Scenarios}
Here some possible scenarios of usage of the system are presented.

\subsection{Scenario 1}
Sean has finished university at 18:00, he has to go back home by train but that day Trenord dediced to stage a walkout. Luckily Sean is registered to the car-sharing service PowerEnJoy and can easily go back home even without train. 
He logs in the app on his mobile phone and looks for a car near his current position: he finds one really close but with a low battery level, so he decides to book another car a little more far but with almost full battery level.
In the while two Sean’s friends, who live near Sean, ask him if he could give them a lift: Sean gladly accepts because he’s a good friend and in this way he can have a discount of 10\% on the ride.
They all reach the booked car within an hour and go back home. 
Sean’s friends, who are not registered to PowerEnJoy, found the ride really pleasant and comfortable and think to register in the near future to PowerEnJoy.


\subsection{Scenario 2}
Sean just came back home by train after university, he’s at train station but it’s a really cold day and so he doesn’t want to walk home. He decides to book a PowerEnJoy car to get home in a fast and comfortable way.
While he walks to reach the booked car, Sean’s mom calls him to inform that she’s coming back from work and she can pick him up.
Then Sean easily cancels his booking without paying any fee.


\subsection{Scenario 3}
Sean has to go to say hello to his friend who works in a pub a bit distant from the city where Sean lives. He decides to take advantage of PowerEnJoy service and so looks for a car to book.
The only available car is quite far, but it’s the only possibility for Sean cause he lent his car to his sister who needed it for work.
He leaves home and walks to reach the booked car.. but there is a problem: Sean is not very good at orienting himself. He has a clear and simple map showed by PowerEnJoy’s app on his mobile phone, but he loses himself anyway.
Sean walks for more than one hour to reach the car but he can’t find it, so PowerEnJoy charges him 1 EUR and his booking is canceled.
Luckily, in the while another PowerEnJoy car becomes available near Sean’s position, so he books it and can finally reach his friend.


\subsection{Scenario 4}
Sean is driving his PowerEnjoy car to get home but forgot about checking the battery level before starting the car ride.
Suddenly he realizes that car’s battery is almost exhausted, so he looks for a safe area equipped with power grid station on the onboard computer, but the nearest area is too far to be reached in time. He’s forced to park the car with battery exhausted on side of the street: he will have to pay the amount of money indicated on the onboard computer of the car plus an additional fee for having exhausted the car's battery. 