\section{Constraints}
\subsection{Regulatory polices}
During the registration phase the user is required to allow PowerEnJoy to manage the sensible data he/she is providing. Moreover, the user need to allow the system to access his current location in order to use the services provided by the platform. All the issues related to the user privacy must follow the state regulations.

\subsection{Hardware limitations}
\begin{itemize}
	\item The user must have access to an Internet connection in order to reserve a car from the web app or the mobile app.
	\item The user must activate the GPS module and have access to a data connection on one of its devices in order to unlock the car once he/she has reached it.
	\item The GPS receiver equipped in the cars must be always active in order to communicate the car location to the system.
	\item All the cars must have an active data connection in order to communicate and receive the necessary information from the system.
\end{itemize}

\subsection{Interfaces to other applications}
\subsubsection{Payment management service}
The system needs to integrate an external service for the menagement of the payment methods. All the major payment methods must be supported by the application, including the most popular credit card circuits (including Visa, MasterCard and American Express) and PayPal.

\subsubsection{Car recovery service}
The system needs to integrate the APIs provided by an external company that is in charge of arranging the cars recovery. In case of particular situation in which the car needs extraordinary assistance, the system alerts the external company.