\section{Assumptions and dependencies}

\begin{itemize}
	\item In order to register, the user must insert his/her credentials, including identity card and driving license.
	\item The system submits in the database the user registered matched with the provided PIN.
	\item Every car is equipped with a sensor that communicates to the system if the car's engine is running or not. The value of this sensor is ON for the former case, OFF for the latter.
	\item Every car is equipped with an onboard computer.
	\item Every car is equipped with a GPS receiver that communicates the car location to the system. The data transmitted to the system corresponds to the geographic coordinates of the car location.
	\item The system can automatically lock and unlock the car.
	\item The car locks the engine until the correct user personal PIN is entered in the onboard computer or when a rental ends.
	\item The car's seats are equipped with a sensor able to detect the presence of a person seated in the car. The signal transmitted to the system is equal to 1 if a person is detected, 0 (zero) otherwise.
	\item The car can inform the system whether the doors are closed or not. If at least one of the door is open, the value transimitted is equal to 0 (zero), 1 otherwise.
	\item The set of safe areas is defined by default in the system.
	\item The set of safe areas provided with power grid stations is defined by default in the system.
	\item The rental cost per minute is defined by default in the system.
	\item The car informs the system about the battery level. The value transmitted is equal to the percentage of the battery charge available. Moreover, the car communicates to the system if the battery is charging or not.
	\item The car informs the system about its component state (e.g. A message is sent in case of engine failure).
	\item An external service is integrated in the system in order to manage billing operations.
	\item An external company is in charge of arranging the cars recovery operations.
\end{itemize}
