% !TEX root = ../../../PPD/main.tex
\chapter{Risk Management}
In this Chapter, all the known risks related to planning, technical and business issues will be discussed. Along with the risks identified, a possible strategy to overcome them and to reduce the probability will be provided.

% Competition with other car-sharing companies
First of all, the most important risk that has been identified is the one related to the possible competition with other car sharing companies. Since at this time there are several companies that operates in the same cities where PowerEnJoy is expected to be deployed, it is important to evaluate all the possible scenarios related to this risk. The strategy to overcome this issue needs to be discussed with the marketing team. Well-planned marketing campaigns, interesting prices and services with respect to other companies and simple processes to learn how to use the service can be good strategies to adopt.

% Government sponsorship
Usually, projects that involves a service for the citizens are sponsored by local governments. It is fundamental to organize meeting with the local authorities in order to make them understand the importance and the benefits that PowerEnJoy would bring to the local communities. It is important to collect guarantees from the local governments about the expected economic investment in PowerEnJoy in order to deliver a complete and well designed product and to avoid wrong budget planning.

% Requirements volatility
Another risk is the one related to the requirements volatility. A thorough requirement elicitation phase is fundamental to collect all the projects specifications before taking any decision about the design or the implementation. PowerEnJoy is an application that can be expanded and integrated with multiple features. For this reason, it is important to come to an agreement with all the stakeholders before any development activities start.

% Modification or closing of the external services
Since PowerEnJoy relies on multiple external service, the malfunction, the modification or the closure of one of those would be a serious issue to deal with. The three main external services integrated in PowerEnJoy are the notification, payments and recovery service. Every services mentioned is fundamental for the correct functioning of the application. For this reason, a thorough investigation must be done in order to select the most reliable and known companies in each of those sectors.

% Deliver a user-friendly application
Although the overall process to take advantage of the PowerEnJoy services is intrinsically quite simple, the QA team must assure that the users will be able to easily learn how to use PowerEnJoy. If the users will face difficulties while approaching the app the first time, the effect could be catastrophic. The strategies that can be exploited to overcome this kind of risk are tests focused on the users, such as A/B and beta testing of the mobile and web application along with the interfaces of the onboard computers.

% Infrastructure reliability
PowerEnJoy must guarantee a 24/7 service. The possible downtimes that could happen if the infrastructure supporting PowerEnJoy would not be available represent a critical risk for the whole system. Important economic losses are expected if long downtimes happen. The strategy that can be applied is to make a thorough analysis of all the possible cloud providers in order to select the most suitable one for the system to be developed and deployed.

% Personnel Turnover and code understanding
Finally, the personnel turnover is a chance that must be considered. Serious delays of the system delivery must be expected if new developers join the project in the middle of the development process. As an example, a certain amount of time must be estimate to let the new employees learn the technologies that are used and how the already developed component works. To overcome this risk the personnel selection phase must be conduct with the right attention and the code base must be fully and high detailed documented.
